### 2017-02-03 paper/chapters/gan.tex
added TODO for modified objective

However, for gradient-based learning $\mathcal{L}_g$ provides poor gradient during learning where the discriminator is able to reject samples from the generator with high confidence.\\
Therefore is in practice often equation \ref{eq:l_g_2} instead of equation \ref{eq:l_g_1} used to optimize the generator.\\

>>>>

However, for gradient-based learning $\mathcal{L}_g$ provides poor gradient during learning \todo[inline]{early in training! show difference.} where the discriminator is able to reject samples from the generator with high confidence.\\
Therefore is equation \ref{eq:l_g_2} more commonly used in practice \todo[inline]{citations! dcgan? improved gan?}.
